A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add garbage collection invocation cases

Instead of freeing dead nodes instantaneously, there exists a \textit{reclaim}
operation which is performed whenever a lookup in the computed-table returns a
dead node $x$. Such a reclaim operation increments the reference count of $x$ and
propagates the reclaim operation to $lo(x)$ and $hi(x)$,
respectively~\cite{BRACE90}. \tbr

>>>>

Instead of freeing dead nodes instantaneously, there exists a \textit{reclaim}
operation which is performed whenever a lookup in the computed-table returns a
dead node $x$. Such a reclaim operation increments the reference count of $x$ and
propagates the reclaim operation to $lo(x)$ and $hi(x)$,
respectively~\cite{BRACE90}.

The garbage collection is executed whenever the load factor (the ratio between
number of keys stored and number of available bins) exceeds 4 after an insertion
and $10\%$ of all OBDD nodes are dead. A garbage collection run deletes all entries
in the computed-table referencing dead nodes, and frees all dead nodes. The sizes
of computed- as well as unique-table are increased if the garbage collection does
not find enough dead nodes. Another event invoking the garbage collection is the
memory overflow of computed- and unique-table, although, the $10\%$-threshold of
dead nodes is used again. In any other case, the garbage collection gives up (and
of course, frees all intermediate nodes). \tbr
